# Reproducible Research Peer Assignment

<br>

## 1. Loading and preprocessing the data

<br>

```{r echo=TRUE}
activity <- read.csv("C:/Users/Administrator/Desktop/coursera/activity.csv",sep = ",",stringsAsFactors = FALSE)
```

<br>

## 2. The mean total number of steps taken per day

<br>

```{r echo=TRUE}
acdate<- seq(from=as.Date("2012-10-01"),by =1,to =as.Date("2012-11-30"))
sumdate <-data.frame()
for(a in as.character(acdate)){sumdate <- rbind(sumdate,sum(activity[activity$date == a,1],na.rm = TRUE))}
perday<- cbind(acdate,sumdate)
colnames(perday) <- c("date","totalsteps")
```

<br>

```{r echo=TRUE,fig.height=4}
hist(perday$totalsteps,xlab = "perday steps")
```

<br>

```{r echo=TRUE}
stepmean <- mean(perday$totalsteps)
stepmedian <- median(perday$totalsteps)
```

<br>

The mean of total number of steps taken per day is **`r stepmean`**

<br>

The median of total number of steps taken per day is **`r stepmedian`**

<br>

<br>

## 3. The average daily activity pattern

<br>

```{r echo=TRUE}
inter <- unique(activity$interval)
interave <- data.frame()
for(i in inter){interave <-rbind(interave,mean(activity[activity$interval == i,1],na.rm = TRUE))}
interave <- cbind(inter,interave)
colnames(interave) <- c("interval","ave")
```

<br>

```{r echo = TRUE,fig.height=4}
interpolt<-plot(x=interave$interval,y=interave$ave,type="l")
whichinter<-subset(interave,ave==max(interave$ave))[,1]
```

<br>

The **`r whichinter`** on average across all the days in the dataset, contains the maximum number of steps

<br>

## 4.Imputing missing values

<br>

```{r echo=TRUE}
totalNA <- sum(is.na(activity$steps))
```

<br>

The total number of missing values in the dataset is **`r totalNA`**

<br>

The strategy for filling in all of the missing values in the dataset is *using the mean for steps taken across all days in 5-minute interval*.

<br>


```{r echo=TRUE}
activity_n <-activity
for(i in 1:17568){
        if(is.na(activity_n[i,1])){
                if(i%%288==0){activity_n[i,1]=interave[288,2]}
                else{
                activity_n[i,1]=interave[i%%288,2]
                }
        }
}
```

<br>

```{r echo=TRUE}
sumdate_n <-data.frame()
for(a in as.character(acdate)){sumdate_n <- rbind(sumdate_n,sum(activity_n[activity_n$date == a,1],na.rm = TRUE))}
perday_n<- cbind(acdate,sumdate_n)
colnames(perday_n) <- c("date","totalsteps")
stepmean_n <- mean(perday_n$totalsteps)
stepmedian_n <- median(perday_n$totalsteps)
hist(perday_n$totalsteps)
answermean <-(stepmean == stepmean_n)
answermedian <- (stepmedian == stepmedian_n)
```

<br>

Does the *mean* total number of steps taken per day differ from the estimate from the first part of the assignment: **`r answermean`**

<br>

Does the *median* total number of steps taken per day differ from the estimate from the first part of the assignment: **`r answermedian`**


<br>

## 5. The differences in activity patterns between weekdays and weekends

<br>

```{r echo=TRUE}
library(chron)
library(dplyr)
activity_w <- cbind(activity,1:17568)
for(i in 1:17568){
        
        if(is.weekend(as.Date(activity[i,2]))){
                activity_w[i,4] <-"weekend"
        }
        else{
                activity_w[i,4] <-"weekdays"
        }
}
colnames(activity_w) <- c("steps","date","interval","week")
```

<br>

```{r echo=TRUE,fig.height=4}
library(lattice)
xyplot(steps~interval | week,data = activity_w,layout= c(1,2),type="l",xlab = "Number of steps")
```

<br>



